\begin{abstract}
    The Kauffman bracket skein algebra (KBSA) of an oriented surface 
    $\Sigma$ is defined as the free module spanned by 
    diagrams of unoriented framed links in $\Sigma$ modulo the 
    Kauffman bracket relations with multiplication defined by 
    stacking diagrams using over crossings. One particular 
    modification of this construction is obtained by instead 
    considering the free module spanned by trivalent 
    graphs embedded in $\Sigma$ modulo the Yamada relations and 
    the same multiplication. This algebra is called the 
    $\mathrm{PGL}_2$ skein algebra (otherwise known as the 
    chromatic skein algebra or graph skein algebra) of $\Sigma$. 
    We compute finite presentations of the $\mathrm{PGL}_2$ skein 
    algebras for the punctured torus and the T-shirt, and a finitely 
    generated presentation and multiplication table of the 
    $\mathrm{PGL}_2$ skein algebra of the torus. Additonally, we 
    show that the $\mathrm{PGL}_2$ skein algebras of the punctured 
    torus and T-shirt embed into their respective KBSAs. We show 
    that this fails for the $\mathrm{PGL}_2$ skein algebra of the 
    torus, which is the first instance of this failing in the 
    literature.
\end{abstract}

\begin{comment}
        Some of this could be good for the introduction in the report!

        The Kauffman bracket skein algebra (KBSA) of an oriented
        surface $\Sigma$ (denoted by $S_q(\Sigma)$ in this paper)
        is the free algebra spanned by diagrams of unoriented framed
        links in $\Sigma$ modulo the Kauffmman bracket relations with
        multiplication defined by stacking diagrams using over crossings.
        Due to work by Khovanov and Frenkel, it is known that $S_q(\mathbb{R}^2)$ is exactly
        the diagrammatic calculus of $U_q(\mathfrak{sl}_2)$ intertwiners.
        The diagrammatic calculus of $U_q(\mathfrak{pgl}_2)$ intertwiners
        is given by the free algebra spanned by diagrams of trivalent ribbon
        graphs in $\mathbb{R}^2$ modulo the Yamada relations. In this way,
        one can generalize the notion of the KBSA of an oriented surface
        $\Sigma$ to the so-called graph skein algebra (otherwise known as the
        chromatic, or $\PGL_2$ skein algebra) of $\Sigma$ denoted
        $S_q^Y(\Sigma)$. It is conjectured that the homomorphism
        $JW: S_q^Y(\Sigma) \to S_q(\Sigma)$ defined by cableing Jones-Wenzl
        indempotents on two strands is injective for all $\Sigma$.
        In this paper, we prove that $JW$ is injective for all oriented
        surfaces with boundary, and not injective for the torus.
        We then compute finite presentations for the graph skein algebras of the torus,
        the punctured torus, and the T-shirt, along with a multiplication
        table for the torus.
\end{comment}
